supplement

### 2019-04-10 TCGA_E9-A1N5_article.Rmd
article rev

---
title: "article_supplementary"
author: "Selcen Ari"
date: "20 Mart 2019"
output: html_document
bibliography: ref.bib
---

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Install the packages which is necessary to obtain and process datasets.
BiocManager::install("SummarizedExperiment", version = "3.8")
library(TCGAbiolinks)
library(SummarizedExperiment)
#install devtools
devtools::install.github(selcenari/ceRNAnetsim)
library(ceRNAnetsim)

@@

+ Obtain the tumor tissue gene expression counts.

@@

+ Obtain the normal tissue gene expression counts.

@@

We used `TCGAbiolinks` package to obtain miRNA expression quantification. The query gives read count of miRNA as isoform chromosome coordination. The data also contains mature miRNA information. So, we processed data to attain -5p -3p isoform information using mirbase release21 dataset.

>>>>

---
title: "article_supplementary"
author: "Selcen Ari"
date: "20 Mart 2019"
output:
  pdf_document: default
  html_document: default
bibliography: ref.bib
---

@@

```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Install the packages which is necessary to obtain and process datasets.
#BiocManager::install("SummarizedExperiment", version = "3.8")
library(TCGAbiolinks)
library(SummarizedExperiment)
#install devtools
devtools::install.github(selcenari/ceRNAnetsim)
library(ceRNAnetsim)
```

@@

+ Obtain to gene expression counts of tumor tissue.

@@

+ Obtain to gene expression counts of normal tissue.

@@

We have used `TCGAbiolinks` package to obtain miRNA expression quantification. The query gives read count of miRNA as isoform chromosome coordination. The data also contains mature miRNA information. So, we processed data to attain -5p -3p isoform information using mirbase release21 dataset.

### 2019-04-10 article.Rmd
article rev

MicroRNAs (miRNAs) that are key regulator of gene expression through various post-transcriptional mechanisms are a family of short non-coding RNAs. Although repression mechanisms of miRNA are not fully understood, exact effect of miRNAs is regulation of direct target/targets negatively. Repressive activities of miRNAs vary depending on many factors that are significant to microRNA:target interactions. These factors include microRNA:target binding energy, binding location in target sequence, base pairing types between miRNA and target, abundance of miRNAs and targets [@grimson_microrna_2007]. Binding energies of miRNA:target complexes vary based on nucleotide context and determine folding stability of complex [@cao_predicting_2012]. It has been demonstrated that the binding energy between miRNA and target indicates stability or affinity of complex [@helwak_mapping_2013] and does not directly determine repressive activity of miRNA [@cao_predicting_2012]. Early studies have argued that 2-8 nt sequence, seed, located in miRNA 5’UTR bind to specific sequence located in 3’UTR of its target [@bartel_micrornas_2004; @lewis_conserved_2005]. In recent studies, it has been shown miRNAs can interact with targets via sequence that located in different region such as 5’UTR or CDS [@hausser_analysis_2013; @helwak_mapping_2013]moore_mirnatarget_2015. These studies also shown that binding location could indicate functionality of miRNA:target interaction or affect profile of target abundance. It has been shown that miRNAs exhibit repressive activity via, 6-8 nt long sequence that is prefectly complementary with targets, seed region at the 5’UTR of miRNAs [@bartel_micrornas:_2009; @grimson_microrna_2007]. On the other hand, some researchers have reported that seed sequence of miRNA can have mismatches or bulged/wobble nucleotides and locates in different region of miRNAs [@hafner_transcriptome-wide_2010; @helwak_mapping_2013]. In addition to all of these, abundance of miRNAs and targets and miRNA:target ratio in cells are determinant for efficiency of miRNA:target interaction [@arvey_target_2010; @bosson_endogenous_2014; @denzler_assessing_2014].

@@

![Workflow for simulation of competing endogenous RNA regulations. Graph object in steps 2-6 is saved and updated continuously.](workflow.jpg){#fig3}

### Defined functions for ceRNA models
We defined the functions that can be used with R programming. Briefly, these functions process a given miRNA:gene dataset and convert to graph object. All values that are significant in miRNA:target interactions are stored in edge variables and processed with formulations that are given in previous section. The functions and steps of approach are explained as following (\autoref{fig3}) :
*Convertion of dataset*: priming_graph function processes the given dataset that includes competing elements in first variable and repressive element in second variable. If the affinity and/or degradation factors are specified in the function, factors are taken into account, are processed with defaults in vice versa. The formulations that are given in equations \eqref{eq:1}-\eqref{eq:5} are performed in this function. This step gives the graph object which contains efficiency values of miRNA:competing target pairs in steady-state in terms of amount. It is assumed that the initial target amounts in the dataset is observed after the reppressive activity of miRNAs in steady-state. *Transition of variables in graph*: In the previous step, the calculations are performed in the edge variables of the graph object. However, the graph object allows to use node variables, while the node features are handled to the graph. In this direction, update_nodes function carries the amount values to node variables This step must be applied with “once” option because it is primary process.
*Trigger change in graph*: The dataset are assumed as steady-state in previous step and the efficieny coefficients are calculated according to this acceptance. In the network that is found in steady-state conditions, the change is applied to the graph object for disturbtion of steady-state. To provide the disturbtion in the network the workflow offer two methods: update_variables and update_how. The first, a new dataset that is contained competing and repressive element names and current values of these can be processed with update_variables. The second option, the amount of the given node name in update_how function can be changed according to “how” argument.
*Updating current values of variables*: After variables updating in edge varibles, these are carried to node variables. Current and previous values of variables are stored as node variables with update_variables function.
*Simulation of competing behavior of targets*: After the change in the steady-state conditions, the network elements try to gain steady-state again. This process progresses as repeating of regulations after the spreading the changes in the network. In this step, simulation of regulations according to given cycle count in simulate function is applied. After each simulation cycle, the miRNA repression values are re-calculated and the current values of competing elements are found and saved. The process is performed in the edge data and at the same time outputs of the calculations are carried from edge to node data.
The node elements in the dataset are handled as two type; repressives (miRNAs) and competings (targets). It is assumed in approach that while targets are degrading or inhibiting by miRNAs continuously, miRNAs reversibly used. If the trigger of the network is a miRNA, it maintains the current value of amount that provides by user. On the contrary, it tries to help this process to provide steady-state through the regulations on its amount, if a competing element is used as a trigger. The functions that are used in the approach are developed with R programming so as can be used with other packages. These are can be found in the github repository [ceRNAnetsim github page](https://github.com/selcenari/ceRNAnetsim) and improved with contributions of others.

@@

![Target regulations with interaction parameters. a) In the steady-state the repression activity of miRNAs on the targets after binding and repression efficiency. b) The changes the repression activities after increasing of G2 expression. c) Perturbation of primary neighborhoods of M1 miRNA (M1 miRNA group). d) Regulation of gene expression of other gene group via triggering target (common target between M1 and M2). ](Fig4.jpg){#fig4}

It has been reported in several studies that miRNA regulatory interactions also is affected different parameters. For example, Xu et. al have investigated the importance of seed pairing type between miRNAs and their targets and target site location by using proteomic dataset [@xu_characterization_2014]. They have proposed that the features of binding between miRNA and target can be critical efficiency of miRNA and can be used to find effective miRNA molecules. In addition, binding energy between miRNA and targets also could be determinant for miRNA efficiency. It has been reported by Breda et. al. that strength of miRNA:target interactions is depended on binding energy of complexes [@breda_quantifying_2015]. As similar to these, Bosson et al. have associated affinity and seed pairing of miRNA target pairs and suggested that number of canonical base pairing is correlated with affinity. For these reasons, we have improved the model with optional interaction parameters that could be useful for understanding of miRNA repression activity. We have explained the model in the same sample dataset with using different factors and simulated via the same change (\autoref{fig4}). When the factors were taken into account in the system, miRNA efficiencies varied as shown in \autoref{fig4}a. Although the miRNA target ratios in initial states were same in comparison with the sample dataset without factors, efficiency of binding and repression have changed. When expression of a gene (G2) increased, expression values of all genes also change differentially because of contribution of efficiency factors (\autoref{fig4} b,c,d).

In regulation of miRNA target sample system (\autoref{fig4}), miRNA (M1) repressive efficiency on the primary triggering gene (G2) is low in steady-state. So it has been observed that the regulatory activities of miRNA efficiencies on the targets are weak after the increase of miRNA target G2. When we ran to model with two fold increasing expression value of common target (G4), the changes of other gene expressions have observed more prominent. Furthermore, folding of expression of target gene that has strong miRNA repression efficiency also resulted in evident perturbation.

The defined miRNA’ number is very low in comparison with defined protein coding genes’ number. So, this results in that the miRNA amounts in the system must be high or targeted RNAs’ amount must be low for effective miRNA activity. We have tried to simulate a real dataset which contains thousands of genes and hundreds of miRNAs. Briefly, we have obtained the datasets and combined these via R programming. We have applied the our approach into integrated dataset using a selected gene. Firstly, we have observed the activities in the iterations and determined behaviours of the network after simulation. As expected, we have observed that the big dataset, compared to those containing a few genes and miRNAs, exhibited cumbersome behaviours and complexity to gain steady-state. We realized that a small change in a system with a large change actually brought many arrangements. This can be explained with the competing groups. Because the genes are targeted with many common miRNAs, and this results in that the common targets exhibits competing behaviours in different groups. On the other hand, the changes of gene expressions were very different. While the change in some of genes were highly evident, somes have changed slightly. So, we have compared two datasets: the tumor gene expression and simulation results. When we analysed comparison of two datasets, we have observed that the results of simulation is not convenient with tumor tissue expression values. The simulation results were not expected to be concordant with tumor tissue expression values because of a single gene could not be responsible for gene regulation in all tissue. Besides, the all other factors such as up/down regulation of miRNAs or other genes were ignored. Of course, it would be more useful to test a dataset that includes gene expression values before and after the regulation of a gene. When we evaluated the suitability of approach, the approach allows different miRNA targets to be considered together and can work with different regulatory elements due to the network structure.

>>>>

MicroRNAs (miRNAs) that are key regulator of gene expression through various post-transcriptional mechanisms are a family of short non-coding RNAs. Although repression mechanisms of miRNA are not fully understood, exact effect of miRNAs is regulation of direct target/targets negatively. Repressive activities of miRNAs vary depending on many factors that are significant to microRNA:target interactions. These factors include microRNA:target binding energy, binding location in target sequence, base pairing types between miRNA and target, abundance of miRNAs and targets [@grimson_microrna_2007]. Binding energies of miRNA:target complexes vary based on nucleotide context and determine folding stability of complex [@cao_predicting_2012]. It has been demonstrated that the binding energy between miRNA and target indicates stability or affinity of complex [@helwak_mapping_2013] and does not directly determine repressive activity of miRNA [@cao_predicting_2012]. Early studies have argued that 2-8 nt sequence, seed, located in miRNA 5’UTR bind to specific sequence located in 3’UTR of its target [@bartel_micrornas_2004; @lewis_conserved_2005]. In recent studies, it has been shown miRNAs can interact with targets via sequence that located in different region such as 5’UTR or CDS [@hausser_analysis_2013; @helwak_mapping_2013] **moore_mirnatarget_2015**. These studies also shown that binding location could indicate functionality of miRNA:target interaction or affect profile of target abundance. It has been shown that miRNAs exhibit repressive activity via, 6-8 nt long sequence that is prefectly complementary with targets, seed region at the 5’UTR of miRNAs [@bartel_micrornas:_2009; @grimson_microrna_2007]. On the other hand, some researchers have reported that seed sequence of miRNA can have mismatches or bulged/wobble nucleotides and locates in different region of miRNAs [@hafner_transcriptome-wide_2010; @helwak_mapping_2013]. In addition to all of these, abundance of miRNAs and targets and miRNA:target ratio in cells are determinant for efficiency of miRNA:target interaction [@arvey_target_2010; @bosson_endogenous_2014; @denzler_assessing_2014].

@@

### Application of model in a breast cancer patient dataset

To determine suitability of method, we have tried to apply model in a real dataset. Firstly, we obtained the miRNA and gene expression datasets of the patient's tumor and normal tissue. We downloaded the high-throughtput experimental datasets which are provided miRNA:gene target pairs with interaction factors by **moore_mirnatarget_2015** and [@helwak_mapping_2013]. We have combined miRNA and gene expression datasets via miRNA:target gene dataset **(Whole steps can be found in Supplementary data(TCGA_E9-A1N5_article.Rmd)**). We selected a gene which is over expressed in tumor tissue with compared to normal tissue. It is pointed out that ABCC1 gene, *Multidrug resistance-associated protein 1*, is one of the most significant factor to develop resistance against chemotherapotic agents[@atalay2008role; @lu2015microrna; @atalay2006multidrug]. So, we selected ABCC1 gene for simulation of integrated dataset. We have detected the iteration that is suitable for ABCC1 gene simulation. After simulation of system via ABCC1 gene with over expression, we have compared simulation results and tumor tissue expression levels.

@@

![Target regulations with interaction parameters. a) In the steady-state the repression activity of miRNAs on the targets after binding and repression efficiency. b) The changes the repression activities after increasing of G2 expression. c) Perturbation of primary neighborhoods of M1 miRNA (M1 miRNA group). d) Regulation of gene expression of other gene group via triggering target (common target between M1 and M2). ](Fig3.jpg){#fig3}

It has been reported in several studies that miRNA regulatory interactions also is affected different parameters. For example, Xu et. al have investigated the importance of seed pairing type between miRNAs and their targets and target site location by using proteomic dataset [@xu_characterization_2014]. They have proposed that the features of binding between miRNA and target can be critical efficiency of miRNA and can be used to find effective miRNA molecules. In addition, binding energy between miRNA and targets also could be determinant for miRNA efficiency. It has been reported by Breda et. al. that strength of miRNA:target interactions is depended on binding energy of complexes [@breda_quantifying_2015]. As similar to these, Bosson et al. have associated affinity and seed pairing of miRNA target pairs and suggested that number of canonical base pairing is correlated with affinity. For these reasons, we have improved the model with optional interaction parameters that could be useful for understanding of miRNA repression activity. We have explained the model in the same sample dataset with using different factors and simulated via the same change (\autoref{fig3}). When the factors were taken into account in the system, miRNA efficiencies varied as shown in \autoref{fig3}a. Although the miRNA target ratios in initial states were same in comparison with the sample dataset without factors, efficiency of binding and repression have changed. When expression of a gene (G2) increased, expression values of all genes also change differentially because of contribution of efficiency factors (\autoref{fig3} b,c,d).

In regulation of miRNA target sample system (\autoref{fig3}), miRNA (M1) repressive efficiency on the primary triggering gene (G2) is low in steady-state. So it has been observed that the regulatory activities of miRNA efficiencies on the targets are weak after the increase of miRNA target G2. When we ran to model with two fold increasing expression value of common target (G4), the changes of other gene expressions have observed more prominent. Furthermore, folding of expression of target gene that has strong miRNA repression efficiency also resulted in evident perturbation. On the other hand, It was observed that Gene2 was weakly affected from change of Gene4 expression because of its weak interaction factors.This also shows that the perturbation iniated element in the system is important parameter. So, we also have developed an approach that is found perturbation efficiencies of elements in dataset. **(see details in Supplementary File(fig1_2app.Rmd)**. When we applied the method on the minimal dataset, while Gene4 is the most efficient element in terms of number of perturbed elements, it have observed that Mir2 is most potent element in the mean of expression change.

The defined miRNA’ number is very low in comparison with defined protein coding genes’ number. So, this results in that the miRNA amounts in the system must be high or targeted RNAs’ amount must be low for effective miRNA activity. We have tried to simulate a real dataset which contains thousands of genes and hundreds of miRNAs. Firstly, we have observed the activities in the iterations and determined behaviours of the network after simulation. As expected, we have observed that the big dataset, compared to those containing a few genes and miRNAs, exhibited cumbersome behaviours and complexity to gain steady-state **(see details in Supplementary File(TCGA_E9-A1N5_article.Rmd)**. We realized that a small change in a system with a large change actually brought many arrangements. This can be explained with the competing groups. Because the genes are targeted with many common miRNAs, and this results in that the common targets exhibit competing behaviours in different groups. On the other hand, the changes of gene expressions were very different. While the change in some of genes were highly evident, somes have changed slightly. So, we have compared two datasets: the tumor gene expression and simulation results. When we analysed comparison of two datasets, we have observed that the results of simulation is not convenient with tumor tissue expression values. The simulation results were not expected to be concordant with tumor tissue expression values because of a single gene could not be responsible for gene regulation in all tissue. Besides, the all other factors such as up/down regulation of miRNAs or other genes were ignored. Of course, it would be more useful to test a dataset that includes gene expression values before and after the regulation of a gene. When we evaluated the suitability of approach, the approach allows different miRNA targets to be considered together and can work with different regulatory elements due to the network structure.

### 2019-04-10 fig1_2app.Rmd
article rev

---
title: "supplement"
author: "Selcen Arı"
date: "7 Nisan 2019"
output: html_document
---

@@

```{r}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene2", 2)%>%
  update_nodes()%>%
  simulate(3)%>%activate(edges)%>%
  as_tibble()%>%
  select(Competing_name,comp_count_list,effect_list)%>%
  unnest()

@@

```{r}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene2", 2)%>%
  update_nodes()%>%
  simulate(3)%>%activate(edges)%>%
  as_tibble()%>%
  select(Competing_name,comp_count_list,effect_list)%>%
  unnest()
```

>>>>

---
title: "supplement"
author: "Selcen Ari"
date: "7 Nisan 2019"
output: html_document
---

### Defined functions for ceRNA models and workflow of method
We defined the functions that can be used with R programming. Briefly, these functions process a given miRNA:gene dataset and convert to graph object. All values that are significant in miRNA:target interactions are stored in edge variables and processed with formulations that are given in previous section. The functions and steps of approach are explained as following (Figure 1) :

*Convertion of dataset*: priming_graph function processes the given dataset that includes competing elements in first variable and repressive element in second variable. If the affinity and/or degradation factors are specified in the function, factors are taken into account, are processed with defaults in vice versa. The formulations that are given in equations (1-5) are performed in this function. This step gives the graph object which contains efficiency values of miRNA:competing target pairs in steady-state in terms of amount. It is assumed that the initial target amounts in the dataset is observed after the reppressive activity of miRNAs in steady-state.

![Workflow for simulation of competing endogenous RNA regulations. Graph object in steps 2-6 is saved and updated continuously.](workflow1.jpg){#fig1}

*Transition of variables in graph*: In the previous step, the calculations are performed in the edge variables of the graph object. However, the graph object allows to use node variables, while the node features are handled to the graph. In this direction, update_nodes function carries the amount values to node variables This step must be applied with “once” option because it is primary process.

*Trigger change in graph*: The dataset are assumed as steady-state in previous step and the efficieny coefficients are calculated according to this acceptance. In the network that is found in steady-state conditions, the change is applied to the graph object for disturbtion of steady-state. To provide the disturbtion in the network the workflow offer two methods: update_variables and update_how. The first, a new dataset that is contained competing and repressive element names and current values of these can be processed with update_variables. The second option, the amount of the given node name in update_how function can be changed according to “how” argument.

*Updating current values of variables*: After variables updating in edge varibles, these are carried to node variables. Current and previous values of variables are stored as node variables with update_variables function.

*Simulation of competing behavior of targets*: After the change in the steady-state conditions, the network elements try to gain steady-state again. This process progresses as repeating of regulations after the spreading the changes in the network. In this step, simulation of regulations according to given cycle count in simulate function is applied. After each simulation cycle, the miRNA repression values are re-calculated and the current values of competing elements are found and saved. The process is performed in the edge data and at the same time outputs of the calculations are carried from edge to node data.

The node elements in the dataset are handled as two type; repressives (miRNAs) and competings (targets). It is assumed in approach that while targets are degrading or inhibiting by miRNAs continuously, miRNAs reversibly used. If the trigger of the network is a miRNA, it maintains the current value of amount that provides by user. On the contrary, it tries to help this process to provide steady-state through the regulations on its amount, if a competing element is used as a trigger. The functions that are used in the approach are developed with R programming so as can be used with other packages. These are can be found in the github repository [ceRNAnetsim github page](https://github.com/selcenari/ceRNAnetsim) and improved with contributions of others.

```{r, message=FALSE, warning=FALSE}
library(ceRNAnetsim)
```

+ load *minsamp* data

@@

## *minsamp* dataset analysis in lack of interaction factors.

Firstly, we have analysed minimal data without interaction factors between miRNA:target.

- 1. We have evaluated graph in the steady state conditions as followings:

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_nodes(once=TRUE)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", title = "Minimal dataset in steady-state conditions")
```

- 2. We have obtained graph after change on Gene2 expression as followings:

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene2", 2)%>%
  update_nodes()%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "Gene2 Upregulation without interaction factors")
```

- 3. We have determined regulations after Gene2 Upregulation:

```{r, message=FALSE, warning=FALSE}

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene2", 2)%>%
  update_nodes()%>%
  simulate_vis(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "Regulations after Gene2 Upregulation", 2)

```
Note that the regulations are colored according to expression changes of present and a previous value. So, it can be observed that whole gene expressions increase in comparison of initial steady-state. The overall regulations of gene expressions are as followings:

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene2", 2)%>%
  update_nodes()%>%
  simulate(2)%>%
  activate(edges)%>%
  as_tibble()%>%
  select(Competing_name,comp_count_list,effect_list)%>%
  unnest()
```

## *minsamp* dataset analysis with interaction factors.

We have made the same analysis in present of interaction factors.

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_nodes(once=TRUE)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", title = "Minimal dataset in steady-state conditions")

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene2", 2)%>%
  update_nodes()%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "Gene2 Upregulation without interaction factors")
```

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene2", 2)%>%
  update_nodes()%>%
  simulate_vis(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "Gene2 Upregulation without interaction factors",2)
```

When the graphs which were resulted from analyses were examined, it was observed that behaviours were same. But, when the results were analysed in terms of expression values, the regulation differences can be observed.

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene2", 2)%>%
  update_nodes()%>%
  simulate(3)%>%
  activate(edges)%>%
  as_tibble()%>%
  select(Competing_name,comp_count_list,effect_list)%>%
  unnest()
```

## Common target perturbation in *minsamp* dataset.

There are hundreds of defined miRNAs for human, so this results in presence of common targets of miRNAs in cells. Therefore, we have analysed perturbation efficiency of common target in *minsamp* dataset.

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene4", 2)%>%
  update_nodes()%>%
  simulate_vis(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "Gene2 Upregulation without interaction factors",2)
```

The common target perturbation  (increasing to two fold at Gene4 expression in presence of interaction factors) resulted in more prominent efficiency at the same conditions (shown in following).

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_nodes(once=TRUE)%>%
  update_how("Gene4", 2)%>%
  update_nodes()%>%
  simulate(3)%>%
  activate(edges)%>%
  as_tibble()%>%
  select(Competing_name,comp_count_list,effect_list)%>%
  unnest()
```

## Determination of perturbation efficiencies efficiencies of elements in system.

```{r, message=FALSE, warning=FALSE}

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)-> sample_graph

find_node_perturbation(sample_graph, how = 2, cycle = 3, limit = 0.1)
